Revisited hidden weight bit function

### 2024-10-31 RevisedHiddenWeight.tex
minor 4.2

\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
\end{Prop}

\begin{remark}
    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers. Naturally, the bound remains valid when the complex number is real, as will be the case in our application.
\end{remark}

\pmnote{I would recall between parentheses somewhere that we denote by $|.|$ the complex norm here, which corresponds to the absolute value on $\R${ \color{blue} Tim :OK, check above remark.}

verify if $w$ and $z$ are coherent.
}

Applying this, we get:

@@

In particular, $d_{n/2,n}(x)=d_n(x)$. 
We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:

@@

\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}

   This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\ee^{\ii\alpha}$ and using that $|w|^2=w\overline w$ for every complex number $w$, we have:
    \begin{align*}
        |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
        &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
        &=6-2\cos2\alpha;
    \end{align*}
    the last equality uses that $\ee^{2\ii\alpha}=\cos2\alpha+\ii\sin2\alpha$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:

    \pmnote{@Tim, add intermediate computation in the following: \color{blue} Tim: Done}

    \[
        |P_{a,t}(z)|^2=\left(|-z^2+2z+1|^2\cdot|1+z|^2\right)^t=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
    \]

    \pmnote{@Tim, for the following, by calculus, you mean using some software? In this case we can add a footnote saying in practice we did it with xxx.

    Can you give a plot of $(\alpha,(6-2\cos2\alpha)(2+2\cos\alpha))$ and add the line corresponding to $y=9/4$?
    \color{blue} Tim: Done}

    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally checked using classical tricks from calculus), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$. The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude  $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
\end{proof}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{trigo_bound.pdf}
	\caption{The function $\alpha\mapsto(6-2\cos2\alpha)(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
    \label{fig:trigo_bound}
\end{figure}

>>>>

\begin{Prop}[Cauchy's estimate \eg~\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
%    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
where $M_R$ is the maximum of the absolute value of $f$, $|f(z)|$ on the circle defined by $|z-w|=R$.
\end{Prop}

%\pmnote{ The point for the remark was to recall that we use the notation "$| \cdot |$" for absolute value over the complex, since before we used it only to denote "cardinal" or absolute value over integers.}

%\begin{remark}
%    Property~\ref{property:cauchy_estimate} is typically employed to bound the absolute value of complex numbers. Naturally, the bound remains valid when the complex number is real, as will be the case in our application.
%\end{remark}

Applying the property, we get:

@@

In particular, $d_{\frac{n}{2},n}(x)=d_n(x)$. 
%We focus on the Walsh spectrum restricted to the slices of any function $d_{t,n}$:
We focus on the restricted Walsh spectrum of any function $d_{t,n}$:

@@

%\pmnote{What is the argument: "maximum implies only one is non-zero" \color{blue} Tim: OK, check above lemma}

%\pmnote{perfect.}

   This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $\dis$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\ee^{\ii\alpha}$ and using that $|w|^2=w\overline w$ for every complex number $w$, we have:
    \begin{align*}
        |-z^2+2z+1|^2&=\left(-\ee^{2\ii\alpha}+2\ee^{\ii\alpha}+1\right)\left(-\ee^{-2\ii\alpha}+2\ee^{-\ii\alpha}+1\right)\\
        &=6-\ee^{2\ii\alpha}-\ee^{-2\ii\alpha}\\
        &=6-2\cos (2\alpha),
    \end{align*}
    where the last equality uses that $\ee^{2\ii\alpha}=\cos(2\alpha)+\ii\sin(2\alpha)$. We similarly obtain that $|1+z|^2=2+2\cos\alpha$. Combining both, we get:   
    \[
        |P_{a,t}(z)|^2=\left(|-z^2+2z+1|^2\cdot|1+z|^2\right)^t=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
    \]

    Since $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$ as shown in Figure~\ref{fig:trigo_bound} (which can also be formally proven using derivatives), we obtain that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$. The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude  $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$, and $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
\end{proof}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{trigo_bound.pdf}
	\caption{Graph of the function $\alpha\mapsto(6-2\cos)2\alpha))(2+2\cos\alpha)$ in blue, and the line $y=2^{9/2}$ in red.}
    \label{fig:trigo_bound}
\end{figure}
